Untitled

### 2021-02-26 scripts/survey1_graphs.Rmd
Commit for modifications

#https://stackoverflow.com/questions/32593434/r-change-row-order
tests <- simulated_survey1_dataset %>% 
  summary_factorlist("q1_city", c("q3_category","q5_nature","q2_employees","q4_sales","q6_customers"),
                     p = FALSE, 
                     add_dependent_label = TRUE,
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     total_col = FALSE) %>%
  rename(
    Responses = ` `
  ) #%>% 
 tests$q1_city <- NULL
#  tests$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
 tests <- tests[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
    mutate(group = c("Total Samples","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","",""))

tests %>% 
  kable(
    caption = "Test",
    booktabs = TRUE,
    linesep = "",
    col.names = 
  )
  mutate(group = c("","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","","")) #%>% 
  kable( tests[,c(4,1,2,3)],caption = "TEST CAPTION",
         booktabs = TRUE,
         valign='t')
    ) %>% 
  kable_styling()

>>>>

#https://stackoverflow.com/questions/32593434/r-change-row-order
f_survey <- simulated_survey1_dataset %>% 
  summary_factorlist("q1_city", c("q3_category","q5_nature","q2_employees","q4_sales","q6_customers"),
                     p = FALSE, 
                     add_dependent_label = TRUE,
                     dependent_label_prefix = "",
                     add_col_totals = TRUE,
                     include_row_missing_col = FALSE,
                     col_totals_rowname = "",
                     total_col = FALSE) %>%
  rename(
    Responses = ` `
  ) #%>% 
 f_survey$q1_city <- NULL
#  f_survey$Responses[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] # Manually change the order of the factor levels to have a better visualization 
 f_survey <- f_survey[c(1:5,9,8,6,7,10,11,13,14,15,12,16,21,17,18,19,20,22),] %>% 
    mutate(` ` = c("Total Samples","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","",""))

f_survey %>% 
  kable(
    caption = "Test",
    booktabs = TRUE,
    linesep = "",
    col.names = 
  )
  mutate(group = c("","Restaurant Category","","Restaurant Nature","","Number of Employees","","","","","Average Monthly Sales","","","","","","Restaurant Capacity","","","","","")) #%>%

  kable( f_survey[,c(4,1,2,3)],caption = "Summary Statistics for First Survey",
         booktabs = TRUE,
         valign='t'
         ) 
  #%>% 
  #  kable_styling(latex_options = "hold_position", protect_latex = FALSE)
